The imprint of global magma oceans on exoplanet demographics

### 2023-03-08 src/tex/ms.tex
ensure section describes results without discussion

\subsection{Synthetic planet sample}\label{sec:syn_planets}
Next, we assigned to the stellar sample planetary systems with frequencies, orbital parameters, and bulk properties derived from the \kepler\ mission.
We adopted the planetary occurrence rates in orbital period and radius recently derived in \citet{Bergsten2022}.
Following \citet{Youdin2011a}, their inferred occurrence rate density can be expressed in the form
\begin{equation}
    \frac{\mathrm{d}^2n}{\mathrm{d}R \, \partial P} = F_0 C_n g(R, P),
\end{equation}
where $F_0$
...
\todo[inline]{GALEN: Briefly describe underlying planet occurrence rates of synthetic population, its Mstar dependency, any caveats or assumptions.}

@@

Accurate retrievals from radius measurements alone require high fractions of greenhouse climate-bearing planets to achieve an accurate constraint on $S_\mathrm{thresh}$.
If, on the other hand, a follow-up campaign adds planetary mass estimates and we fit the signal in bulk density space, useful constraints are possible under more pessimistic conditions.
A sample containing only planets around M~dwarf yields a performance comparable to that of the overall sample.

>>>>

\subsection{Synthetic planet sample}\label{sec:syn_planets}

Next, we assigned to the stellar sample planetary systems with frequencies, orbital parameters, and bulk properties derived from the \kepler\ mission.
We adopted the planetary occurrence rate model from \citet{Bergsten2022}, which defines the occurrence of small planets in radius and orbital period. Following \citet{Youdin2011a}, their inferred occurrence rate density can be expressed in the form:
\begin{equation}
    \frac{\mathrm{d}^2n}{\mathrm{d}R \, \partial P} = F_0 C_n g(R, P),
\end{equation}
where $F_0$ represents the average number of planets per star and $C_n$ is a normalization constant. The shape function $g(R,P)$ describing the occurrence distribution is the same as in \citet{Bergsten2022}. The functional form and stellar-mass dependent parameters (including a new fit to the sample of \kepler\ planets with hosts below $0.56\,M_{\odot}$) are included in \bioverse\ as the prominent planet-generation model; the original model based on SAG13 occurrence rates is preserved as a legacy feature.

With this updated distribution function, planets are generated as in the original \bioverse\ paper, but with an additional stellar mass dependence (for a star of a given mass, the relevant model parameters from the bin containing that mass are used). In summary, stars are assigned a number of planets in accordance with $F_0$, with planet parameters randomly drawn in proportion to the occurrence distribution function evaluated over a grid of radii and orbital periods.
% \todo[inline]{GALEN: Briefly describe underlying planet occurrence rates of synthetic population, its Mstar dependency, any caveats or assumptions.}
\todo[inline]{GALEN: The most relevant assumption of using our model is that, at the relevant fluxes (I think), we predict that super-Earths are pretty common. I think the "drop" in our model where super-Earths become less common happens at later fluxes than what is relevant in this paper... Let's double check this, and add a note in the first paragraph about it?.}

@@

We find that retrievals from radius measurements alone require high fractions of greenhouse climate-bearing planets to achieve an accurate constraint on $S_\mathrm{thresh}$:
Dilution factors $f_\mathrm{rgh} \gtrsim 0.5$ yield posterior probability distributions that are condensed at the order of magnitude of the true value; accurate constraints to within $\pm 0.25\,\mathrm{dex}$ of the truth are reached only from $f_\mathrm{rgh} \approx 0.8$.

In contrast, if planet masses are available and the hypothesis test is conducted in bulk density space, useful constraints emerge already from about $f_\mathrm{rgh} \approx 0.35$.
Accuracy and precision of the retrievals are improved.

A sample containing only planets around M~dwarf yields a very similar performance, which is because these planets contribute most to the statistical power of the retrieval.
